When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-23 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
inserted SCA plot

Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variables in their raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varies between subjects, but there are no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
The ICC of the null model indicated that there is a correlation of `r $r=round(model0_h2b_ICC, digits = 3)$` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
The final model had an effect size of `r $f^{2} = round(h2b_level_f2, digits = 2)$` for the *n*-back levels and `r $f^{2} = round(h2b_dprime_f2, digits = 2)$` for *d'*, which are considered large and small, respectively [@Cohen1992].
The effect size of the median RT was `r $f^{2} = format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)$`.

@@

JZ, CS, and AS conceptualized the study and acquired funding.
JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.

>>>>

Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variables in their raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varies between subjects, but there are no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
The ICC of the null model indicated that there is a correlation of `r $r=round(model0_h2b_ICC, digits = 3)$` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table\ \@ref(tab:H2b-results)

```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
kable(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        booktabs = T,                          # no vertical lines
        escape = F,                            # correctly print special characters)
        align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
             escape = F,                    # correctly print special characters
             threeparttable = T)            # line breaks in the footnote
```

The model had an effect size of `r $f^{2} = round(h2b_level_f2, digits = 2)$` for the *n*-back levels and `r $f^{2} = round(h2b_dprime_f2, digits = 2)$` for *d'*, which are considered large and small, respectively [@Cohen1992].
This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The effect size of the median RT was `r $f^{2} = format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)$`.

To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis.

INSERT FIGURE 2 HERE

```{r sca-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the middle panel shows the p-value of the full model, and the upper panel the beta coefficient as a line and its standard deviation as a vertical box. The colourbar indicates the BF10.", fig.pos="H"}

  print(sca_plot)

@@

JZ, CS, and AS conceptualized the study and acquired funding.
JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
JZ, CS, and CK did the formal analysis.
JZ visualized the results, and prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.
